When surveying a new field, researchers often want an overview look at the important papers in the field, how they are related, and how popular trends in topics or techniques have been evolving over the years. Traditional search engines such as Google Scholar and digital libraries such as the ACM's can alleviate the task, but only when the researcher has a good idea of what he should look for. Even then, the information obtained from those tools at any given moment is not only too specific but also presented in a non-visual form, making it difficult for the user to see a bigger picture.

Being both interested in doing research in computer graphics, in this project we aim to develop a tool to visualize connections between papers published over the years in SIGGRAPH, the most important conference in computer graphics. The tool should show in one place: the citation relationships among SIGGRAPH papers, important papers in each sub-field, prolific authors and their collaboration patterns, popular topics and methods in recent years, and active research institutions in each sub-field. It is our hope that such a tool can be particularly helpful to someone who wants to survey a field and summarize major results. It could also help new researchers in finding not only interesting problems to work on but also pointers to relevant publications for reference. Lastly, prospective graduate students can use information provided by the tool to make more informed decision in their application process.